---
title: "R Notebook"
output: html_notebook
---
Loading the installed packages

```{r}
library(ggplot2)
library(forecast)
library(plotly)
library(ggfortify)
library(tseries)
library(gridExtra)
library(docstring)
library(readr)
library(here)
library(timeSeries)
library(packrat)
here()
```

The data of 6 TimeSeries Data of monthly adjusted closing prices is retrieved from yahoo finance from 1996-01-01 to 2019-09-22. Loading the monthly prices, removing and replacing the missing values.

6 TimeSeries Data are,

1) BSE-500
2) BSE-200
3) BSE-100
4) High Market Cap Index - RELIANCE
5) Medium  Market Cap Index - GILLETTE
6) Small Market Cap Index - SPICEJET

```{r}
#S&P BSE_500 INDEX 

BSE_500 <- tseries::get.hist.quote(instrument="BSE-500.BO", start="1996-01-01",
                      end="2019-09-29", quote="AdjClose",
                      provider="yahoo", origin="1970-01-01",
                      compression="m", retclass="zoo")
nrow(BSE_500)
BSE_500 <- na.omit(BSE_500)
BSE_500.ts <- ts(BSE_500)

#S&P BSE 200 INDEX 

BSE_200 <- tseries::get.hist.quote(instrument="BSE-200.BO", start="1996-01-01",
                      end="2019-09-29", quote="AdjClose",
                      provider="yahoo", origin="1970-01-01",
                      compression="m", retclass="zoo")
nrow(BSE_200)
BSE_200 <- na.omit(BSE_200)
BSE_200.ts <- ts(BSE_200)

#S&P BSE 100 INDEX (BSE-100.BO)

BSE_100 <- tseries::get.hist.quote(instrument="BSE-100.BO", start="1996-01-01",
                      end="2019-09-29", quote="AdjClose",
                      provider="yahoo", origin="1970-01-01",
                      compression="m", retclass="zoo")
nrow(BSE_100)
BSE_100 <- na.omit(BSE_100)
BSE_100.ts <- ts(BSE_100)

#High Cap Index- Reliance Industries Limited (RELIANCE.BO)

Reliance <- tseries::get.hist.quote(instrument="RELIANCE.BO", start="1996-01-01",
                      end="2019-09-29", quote="AdjClose",
                      provider="yahoo", origin="1970-01-01",
                      compression="m", retclass="zoo")
nrow(Reliance)
Reliance <- na.omit(Reliance)
nrow(Reliance)

# Medium Cap Index-L&T Finance Holdings Limited (L&TFH.BO)

GILLETTE <- tseries::get.hist.quote(instrument="GILLETTE.BO", start="1996-01-01",
                      end="2019-09-29", quote="AdjClose",
                      provider="yahoo", origin="1970-01-01",
                      compression="m", retclass="zoo")
nrow(GILLETTE)
GILLETTE <- na.omit(GILLETTE)
GILLETTE.ts <- ts(GILLETTE)

#Small Cap Index- SPICEJET Limited (SPICEJET.BO)

SPICEJET <- tseries::get.hist.quote(instrument="SPICEJET.BO", start="1996-01-01",
                      end="2019-09-22", quote="AdjClose",
                      provider="yahoo", origin="1970-01-01",
                      compression="m", retclass="zoo")
nrow(SPICEJET)
SPICEJET <- na.omit(SPICEJET)
SPICEJET.ts <- ts(SPICEJET)

```

```{r}

BSE_500_training <- ts(BSE_500, start=c(1996, 1), end=c(2018, 12), freq=12)
BSE_200_training <- ts(BSE_200, start=c(1996, 1), end=c(2018, 12), freq=12)
BSE_100_training <- ts(BSE_100, start=c(1996, 1), end=c(2018, 12), freq=12)
Reliance_training <- ts(Reliance, start=c(1996, 1), end=c(2018, 12), freq=12)
GILLETTE_training <- ts(GILLETTE, start=c(1995, 1), end=c(2018, 12), freq=12)
SPICEJET_training <- ts(SPICEJET, start=c(1996, 1), end=c(2018, 12), freq=12)

```


```{r}

BSE_500.ts<-ts(BSE_500,start=c(2006, 1),frequency = 12)
BSE_200.ts<-ts(BSE_200,start=c(2006, 1),frequency = 12)
BSE_100.ts<-ts(BSE_100,start=c(2006, 1),frequency = 12)
Reliance.ts<-ts(Reliance,start=c(2006, 1),frequency = 12)
GILLETTE.ts<-ts(GILLETTE,start=c(2006, 1),frequency = 12)
SPICEJET.ts<-ts(SPICEJET,start=c(2006, 1),frequency = 12)

```


```{r}
library(TTR)
here()
decomp <- decompose(BSE_500.ts)
BSE_500dec <- decompose(BSE_500.ts)
plot(BSE_500dec)

```


```{r}
adf.test(BSE_500_training)
```

P value is greater than 0.05.So, our time series is not stationary. To make it stationary, we take the first difference of the data

Plot Auto correlation and Partial correlation using ACF & PACF

```{r}
#1st difference
tsDiff_BSE_500_training <- diff(BSE_500_training)
adf.test(tsDiff_BSE_500_training)
```

P value is significant as it is less than 0.05 hence Time Series is Stationary


```{r}
acf(tsDiff_BSE_500_training)
pacf(tsDiff_BSE_500_training)
```


```{r}
decomp <- decompose(BSE_200.ts)
BSE_200dec <- decompose(BSE_200.ts)
plot(BSE_200dec)
```

```{r}
adf.test(BSE_200_training)
```
P value is significant as it is less than 0.05 hence Time Series is Stationary

```{r}
acf(BSE_200_training)
pacf(BSE_200_training)

```


```{r}

BSE_100dec <- decompose(BSE_100.ts)
plot(BSE_100dec)

```

```{r}
adf.test(BSE_100_training)
```

P value is significant as it is less than 0.05 hence Time Series is Stationary

```{r}
acf(BSE_100_training)
pacf(BSE_100_training)
```


```{r}
decomp <- decompose(Reliance.ts)
Reliancedec <- decompose(Reliance.ts)
plot(Reliancedec)

```

```{r}
adf.test(Reliance_training)

```

P value is greater than 0.05.So, our time series is not stationary. To make it stationary, we take the first difference of the data

```{r}
#1st difference
tsDiff_Reliance_training <- diff(Reliance_training)
adf.test(tsDiff_Reliance_training)

```
P value is significant as it is less than 0.05 hence Time Series is Stationary

```{r}
acf(tsDiff_Reliance_training)
pacf(tsDiff_Reliance_training)
```



```{r}
decomp <- decompose(GILLETTE.ts)
GILLETTEdec <- decompose(GILLETTE.ts)
plot(GILLETTEdec)

```


```{r}
adf.test(GILLETTE_training)

```

P value is greater than 0.05.So, our time series is not stationary. To make it stationary, we take the first difference of the data

```{r}
#1st difference
tsDiff_GILLETTE_training <- diff(GILLETTE_training)
adf.test(tsDiff_GILLETTE_training)

```

P value is significant as it is less than 0.05 hence Time Series is Stationary

```{r}
acf(tsDiff_GILLETTE_training)
pacf(tsDiff_GILLETTE_training)
```

P value is significant as it is less than 0.05 hence Time Series is Stationary

```{r}
decomp <- decompose(SPICEJET.ts)
SPICEJETdec <- decompose(SPICEJET.ts)
plot(SPICEJETdec)
```


```{r}
adf.test(SPICEJET_training)
```

P value is greater than 0.05.So, our time series is not stationary. To make it stationary, we take the first difference of the data

```{r}
#1st difference
tsDiff_SPICEJET_training<- diff(SPICEJET_training)
adf.test(tsDiff_SPICEJET_training)
```

P value is significant as it is less than 0.05 hence Time Series is Stationary

```{r}
acf(tsDiff_SPICEJET_training)
pacf(tsDiff_SPICEJET_training)

```

Insights from above Time Series Analysis od training data

1) BSE-500 - Time Series is stationary after first difference
2) BSE-200 - Time Series is stationary
3) BSE-100 - Time Series is stationary
4) High Market Cap Index - RELIANCE - After first difference Time Series is stationary
5) Medium  Market Cap Index - GILLETTE- After first difference Time Series is stationary
6) Small Market Cap Index - SPICEJET- After first difference Time Series is stationary



```{r}
auto.arima(BSE_500_training, trace = TRUE)

fit1 <- Arima(BSE_500_training, order = c(1,1,0),
	include.drift = TRUE)
summary(fit1)
fit1$aic
fit1$bic
attributes(fit1)

plot(forecast(fit1,h = 12, level = (99.5)))
forecast(fit1, h = 12, level = (99.5))

```

#BSE-500

[AIC] 4379.453
[BIC] 4390.303
re-fitting the best model(s) without approximations and taking (1,1,0)
The forecast from Arima with drift gives the forecasted values with upper boundary and lower boundary values.



```{r}
auto.arima(BSE_200_training, trace = TRUE)

fit2 <- Arima(BSE_200_training, order = c(1,0,1),
	include.drift = TRUE)
summary(fit2)
fit2$aic
fit2$bic
attributes(fit2)

plot(forecast(fit2,h = 12, level = (99.5)))
forecast(fit2, h = 12, level = (99.5))
```

#BSE-200

[AIC] 4329.65
[BIC] 4347.752
re-fitting the best model(s) without approximations and taking (1,0,1)
The forecast from Arima with drift gives the forecasted values with upper boundary and lower boundary values.


```{r}
auto.arima(BSE_100_training, trace = TRUE)

fit3 <- Arima(BSE_100_training, order = c(2,0,0),
	include.drift = TRUE)
summary(fit3)
fit3$aic
fit3$bic
attributes(fit3)

plot(forecast(fit3,h = 12, level = (99.5)))
forecast(fit3, h = 12, level = (99.5))

```

#BSE-100

[AIC] 4341.203
[BIC] 4359.305
re-fitting the best model(s) without approximations and taking (2,0,0)
The forecast from Arima with drift gives the forecasted values with upper boundary and lower boundary values.


```{r}
auto.arima(Reliance_training, trace = TRUE)

fit4 <- Arima(Reliance_training, order = c(3,1,2),
	include.drift = TRUE)
summary(fit4)
fit4$aic
fit4$bic
attributes(fit4)

plot(forecast(fit4,h = 12, level = (99.5)))
forecast(fit4, h = 12, level = (99.5))
```

#Reliance

[AIC] 3395.683
[BIC] 3421
re-fitting the best model(s) without approximations and taking (3,1,2)
The forecast from Arima with drift gives the forecasted values with upper boundary and lower boundary values.


```{r}
auto.arima(GILLETTE_training, trace = TRUE)

fit5 <- Arima(GILLETTE_training, order = c(0,1,0),
	include.drift = TRUE)
summary(fit5)
fit5$aic
fit5$bic
attributes(fit5)

plot(forecast(fit5,h = 12, level = (99.5)))
forecast(fit5, h = 12, level = (99.5))
```

#GILLETTE

[AIC] 4184.484
[BIC] 4191.803
re-fitting the best model(s) without approximations and taking (0,1,0)
The forecast from Arima with drift gives the forecasted values with upper boundary and lower boundary values.

```{r}
auto.arima(SPICEJET_training, trace = TRUE)

fit6 <- Arima(SPICEJET_training, order = c(0,1,0),
	include.drift = TRUE)
summary(fit6)
fit6$aic
fit6$bic
attributes(fit6)

plot(forecast(fit6,h = 12, level = (99.5)))
forecast(fit6, h = 12, level = (99.5))
```


#SPICEJET

[AIC] 1907.925
[BIC] 1915.158
re-fitting the best model(s) without approximations and taking (0,1,0)
The forecast from Arima with drift gives the forecasted values with upper boundary and lower boundary values.

The model with lower AIC and BIC values will be preferred which is Spicejet in the above case.
































